% References
\newpage
\bibliographystyle{unsrt}
%%% Comment out this section when you \bibliography{references} is enabled.
\begin{thebibliography}{1}

  \bibitem{book1}
  Cedric Villani. Topics in optimal transportation. Graduate Studies in Mathematics Series. American Mathematical Society, 2003.

  \bibitem{book2}
  Cedric Villani. Optimal transport: old and new, volume 338. Springer Verlag, 2009.

  \bibitem{book3}
  Filippo Santambrogio. Optimal transport for applied mathematicians. Birkhauser, 2015.

  \bibitem{book4}
  Gabriel Peyré and Marco Cuturi. Computational Optimal Transport. Foundations and Trends in Machine Learning, 11(5-6), 2019, pp.355-607.
  
  \bibitem{article1}
  Gerber, Samuel, and Mauro Maggioni. Multiscale strategies for computing optimal transport. The Journal of Machine Learning Research 18.1 (2017): 2440-2471.

  \bibitem{article2}
  Schrieber, Jörn, Dominic Schuhmacher, and Carsten Gottschlich. Dotmark–a benchmark for discrete optimal transport. IEEE Access 5 (2016): 271-282.

  \bibitem{Arjovsky2017}
  Arjovsky, Martin, Soumith Chintala, and Léon Bottou. "Wasserstein gan." arXiv preprint arXiv:1701.07875 (2017).

  \bibitem{book10}
  Yu. Nesterov, Introductory Lectures on Conves Optimization. A
  Basic Course (2004).

  \bibitem{book11}
  B. T. Polyak, Introduction to Optimization (1987).

  \bibitem{book12}
  S. Boyd, lecture notes and slides for EE364b, Convex Optimization II.

  \bibitem{book13}
  J.-B. Hiriart-Urruty, C. Lemar echal, Convex Analysis and
Minimization Algoritms (1993).

  \bibitem{book14}
  D.P. Bertsekas, Constrained Optimization and Lagrange
Multiplier Methods (1982)

  \bibitem{book15}
  O. Güler, Augmented Lagrangian algorithm for linear
programming, JOTA (1992)

  \bibitem{manual1}
  Manual for MOSEK Optimization Toolbox for MATLAB, Release 8.1.0.82

  \bibitem{gurobi}
  Documentation of Gurobi, 2019
  
  \bibitem{dotdataset}
  Schuhmacher, Dominic; Schrieber, Jörn; Gottschlich, Carsten (2016): 
    DOTmark v1.0. figshare. Dataset. 
    https://doi.org/10.6084/m9.figshare.4288466.v1

\end{thebibliography}